FoRTE baseline

### 2019-07-11 analysis/paper/paper.Rmd
Update references, add GH and OSF links to colophon

>>>>

View this project on GitHub in repository [ashiklom/fortebaseline](https://github.com/ashiklom/fortebaseline)
(This manuscript file is in [`analysis/paper/paper.Rmd`](https://github.com/ashiklom/fortebaseline/blob/master/analysis/paper/paper.Rmd)).
and in Open Science Framework (OSF) at https://osf.io/dznuf/ .
